TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
quadratic label description

Quadratic label vectors for the two models that we will build:
\begin{eqnarray}
\ell_{n} &=& [1, \, SPT, \, SPT^{2}]
\\
\ell_{n} &=& [1, \, T_{\rm eff}, \, [Fe/H], \, T_{\rm eff} \cdot [Fe/H], \, [Fe/H]^{2}]
,
\end{eqnarray}
where the first is for JB WHAT and the second is for JB WHAT?

>>>>

We apply a quadratic parameterization of the model such that the label vectors for the two models that we will build are:
\begin{eqnarray}
\ell_{n} &=& [1, \, SPT, \, SPT^{2}] \label{eqn:spt}
\\
\ell_{n} &=& [1, \, T_{\rm eff}, \, [Fe/H], \, T_{\rm eff}^2, \, T_{\rm eff} \cdot [Fe/H], \, [Fe/H]^{2}] \label{eqn:physical}
,
\end{eqnarray}
Equation (\ref{eqn:spt}) is the label vector for the spectral type model with a highest order of 2, and equation (\ref{eqn:physical}) is the label vector for the physical parameter model of order 2 including a cross term between the two labels.
